method

### 2022-02-22 06_Paper/ER-ED/method.Rmd
fixed typo
corrected typo

The online survey contains a number of questionnaires: General psychological well-being is assessed using the German version of the WHO-5 scale [@Bech2004; @Braehler2007].
To capture the construct of resilience, the German version 10-item-form of the Connor-Davidson resilience Scale (CD-RISC)[@Connor2003,@Campbell-Sills2007; @Sarubin2015] is used.
Dispositional use of ER is assessed using the German version of the Emotion Regulation Questionnaire (ERQ) [@GrossJohn2003; @Abler2009].
For the assessment of ER ability we use the Flexible Emotion Regulation Scale (FlexER) [@Doerfel2019].
Implicit theories of willpower in emotion control are assessed using the implicit theories questionnaire from @Bernecker2017.
To assess Need for Cognition, the German version short form of the Need for Cognition Scale [@Cacioppo1982; @Bless1994] is used.
To assess self-control, sum scores of the German versions of the following questionnaires are used [@Paschke2016]: the Self-Regulation Scale (SRS) [@Schwarzer1999], the Brief Self-Control Scale (BSCS) @Tangney2004; @Sproesser2011], and the Barratt Impulsiveness Scale (BIS-11) [@Patton1995; @Hartmann2011].
Attentional control is assessed using the Attentional Control Scale (ACS) [@Derryberry2002].
<!-- Not sure whether you can state this so briefly without giving more detailed information on, e.g., sample items, the scale on which answers are recorded (e.g., -3 ... +3), the reliability of the measures. -->

@@

Sample size calculation is done using *G\*Power* [@Faul2007; @Faul2009].
In a meta-analysis of Zaehringer and colleagues [-@Zaehringer2020], effect sizes of ER on peripheral-physiological measures were reported.
To find an effect of $d=-0.32$ of ER on *corrugator* muscle activity with $\alpha=.05$ and $\beta=.95$, data of least $N=85$ have to be analyzed.
Power analyses of all other hypotheses yielded smaller sample sizes.
However, if participants withdraw from study participation, technical failures occur, or experimenter considers the participant for not suitable for study participation (e.g., because the participant does not follow instructions or shows great fatigue), respective data will also be excluded from further analyses.
Therefore, we aim to collect data of 90 participants.
Detailed information on power calculation for each hypothesis can be found in the design table.

>>>>

The online survey contains a number of questionnaires: General psychological well-being is assessed using the German version of the WHO-5 scale [@Bech2004; @Braehler2007].
To capture the construct of resilience, the German version 10-item-form of the Connor-Davidson resilience Scale (CD-RISC)[@Connor2003,@Campbell-Sills2007; @Sarubin2015] is used.
Habitual use of ER is assessed using the German version of the Emotion Regulation Questionnaire (ERQ) [@GrossJohn2003; @Abler2009].
For the assessment of ER ability we use the Flexible Emotion Regulation Scale (FlexER) [@Doerfel2019].
Implicit theories of willpower in emotion control are assessed using the implicit theories questionnaire from @Bernecker2017.
To assess Need for Cognition, the German version short form of the Need for Cognition Scale [@Cacioppo1982; @Bless1994] is used.
To assess self-control, sum scores of the German versions of the following questionnaires are used [@Paschke2016]: the Self-Regulation Scale (SRS) [@Schwarzer1999], the Brief Self-Control Scale (BSCS) @Tangney2004; @Sproesser2011], and the Barratt Impulsiveness Scale (BIS-11) [@Patton1995; @Hartmann2011].
Attentional control is assessed using the Attentional Control Scale (ACS) [@Derryberry2002].
<!-- Not sure whether you can state this so briefly without giving more detailed information on, e.g., sample items, the scale on which answers are recorded (e.g., -3 ... +3), the reliability of the measures. -->

@@

Sample size calculation is done using *G\*Power* [@Faul2007; @Faul2009].
In a meta-analysis of Zaehringer and colleagues [-@Zaehringer2020], effect sizes of ER on peripheral-physiological measures were reported.
To find an effect of $d=-0.32$ of ER on *corrugator* muscle activity with $\alpha=.05$ and $\beta=.95$, data of least $N=85$ have to be analyzed.
Power analyses of all other hypotheses yielded smaller sample sizes.
However, if participants withdraw from study participation, technical failures occur, or experimenter considers the participant for not suitable for study participation (e.g., because the participant does not follow instructions or shows great fatigue), respective data will also be excluded from further analyses.
Therefore, we aim to collect data of 90 participants.
Detailed information on power calculation for each hypothesis can be found in the [design table](#DesignTable).
